Abalone MSE Data files

### 2023-07-12 data-raw/vignettefiles/the_data_files.Rmd
Now use of refperiodCE is optional. No EWN.

---
title: "Comparison of MSE Scenarios"
author: "Malcolm Haddon, ..."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comparison of MSE Scenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

suppressPackageStartupMessages({
library(aMSE)
library(TasHS)
library(codeutils)
library(hplot)
library(knitr)
library(makehtml)
library(captioner)
})

@@

dbdir <- getDBdir()
ddir <- paste0(dbdir,"/A_CodeUse/aMSEDoc/") 
prefixdir <- paste0(dbdir,"/A_CodeUse/aMSEUse/scenarios/")

@@

This document is part of the more formal documentation for the R package __aMSE__, which aims to provide a common modelling framework to test abalone harvest strategies. Being one of the vignettes included in the package it should be regarded as a living, adaptable document that will be modified as experience increases around different jurisdictions, and the authorship should be expected to alter accordingly as different people contribute. It is assumed in this vignette that the reader has managed to run a number of scenarios that they then wish to compare.

### Saving the Output from aMSE

One concept in the use of __aMSE__ is that of the _rundir_, which is the directory into which all the data files are placed and all the results, plots, and html files will be placed. However, a typical scenario MSE run will include a final line where the output from the _do_MSE()_ function is saved into an _outdir_. The _outdir_ should not be on a cloud service shared with others as the output objects can be large (gigabytes). so typically it will point to a directory on a fast hard-drive or SSD that should be used to identify a given series of scenarios for comparison. The actual scenario name is usually encapsulated in the _postfixdir_ name:

```{r echo=TRUE, eval=FALSE}
# A subset of commands to run a given scenario
postfixdir <- "BC"                   # BC stands for basecase
rundir <- filenametopath(prefixdir,postfixdir)
outdir <- "C:/aMSE_scenarios/BC/"
confirmdir(rundir,ask=FALSE)     # check to see if it already exists
confirmdir(outdir,ask=FALSE)     # and if not create it without asking.

hsargs <- list(mult=0.1, # expansion factor for cpue range when calc the targqnt
               wid = 4, # number of years in the grad4 PM
               targqnt = 0.55, # quantile defining the cpue target
               maxtarg = c(150,150,150,150,150,150,150,150), # max cpue Target
               pmwts = c(0.65,0.25,0.1),  # relative weights of PMs
               hcr = c(0.25,0.75,0.8,0.85,0.9,1,1.05,1.1,1.15,1.2), # hcr multipliers
               startCE = 2000, # used in constant reference period HS
               endCE = 2019,   # used in constant reference period HS
               metRunder = 1,  # should the metarules be used. o =
               metRover = 1,   # use metarules
               decrement=1, # use fishery data up to the end of the time series
               pmwtSwitch = 0, # number of years after reaching the targCE to
               stablewts = c(0.4, 0.5, 0.1), # replace pmwts with stablewts
               hcrname="mcdahcr",     # the name of the HCR used
               printmat=NULL)

out <- do_MSE(rundir,controlfile,hsargs=hsargs,hcrfun=mcdahcr,
              sampleCE=tasCPUE,sampleFIS=tasFIS,sampleNaS=tasNaS,
              getdata=tasdata,calcpopC=calcexpectpopC,makeouthcr=makeouthcr,
              hcrscoreoutputs=extractandplotscores,HSPMs=getcpueHS,
              fleetdyn=NULL,interimout=c(outdir,postfixdir),
              varyrs=7,startyr=38,verbose=TRUE,ndiagprojs=4,cutcatchN=56,
              matureL=c(40,170),wtatL=c(50,200),mincount=120,
              includeNAS = FALSE,depensate=0,kobeRP=c(0.4,0.2,0.15))

makeoutput(out,rundir,postfixdir,controlfile,hsfile="TasHS Package",
           openfile=TRUE,verbose=FALSE)

save(out,file=paste0(outdir,postfixdir,".RData"))  # the results are saved
```

## Making comparisons

>>>>

---
title: "Abalone MSE Data files"
author: "Malcolm Haddon, ..."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Abalone MSE Data files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

library(aMSE)
library(codeutils)
library(hplot)
library(knitr)
library(captioner)

@@

if (dir.exists("C:/Users/Malcolm/Dropbox")) {
  ddir <- "C:/Users/Malcolm/Dropbox/A_CodeUse/aMSEUse/documentation/"
} else {
  ddir <- "C:/Users/User/Dropbox/A_CodeUse/aMSEUse/documentation/"
}

@@

This document is part of the more formal documentation for the R package __aMSE__, which aims to provide a common modelling framework to test abalone harvest strategies. Being one of the vignettes included in the package it should be regarded as a living, adaptable document that will be modified as experience increases around different jurisdictions, and the authorship should be expected to alter accordingly as different people contribute.

## Stages of an MSE Run
